Supplementary Materials for Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019

### 2023-03-13 products/paper/main.qmd
Add footnote to main text regarding issue #33

The probability of being CBEG also increases with the student's current grade, so I include fixed effects for the current grade of the student. Additionally, as @fig-year-grade shows, the percent of students who are CBEG has declined over time, but this decline has been much more substantial at higher grade levels. For the elementary grades, there is no evidence of a decline at all. To account for this grade-specific decline in the models I include an interaction between a linear year term and current grade. Sensitivity analysis showed that this functional form was preferred by the Bayesian information criterion to models with no interaction and a model with interaction terms that treated year as a categorical variable. I also considered a similar interaction between state and year, but this model was not preferred.

>>>>

The probability of being CBEG also increases with the student's current grade, so I include fixed effects for the current grade of the student. Additionally, as @fig-year-grade shows, the percent of students who are CBEG has declined over time, but this decline has been much more substantial at higher grade levels. For the elementary grades, there is no evidence of a decline at all. To account for this grade-specific decline in the models I include an interaction between a linear year term and current grade. Sensitivity analysis showed that this functional form was preferred by the Bayesian information criterion to models with no interaction and a model with interaction terms that treated year as a categorical variable. I also considered a similar interaction between state and year, but this model was not preferred.[^yeargrade]

[^yeargrade]: The supplementary materials provide, for each specification, the BIC scores and marginal probabilities of being clearly behind expected grade for each racial group. The marginal probabilities for each racial group are almost identical across specifications, indicating that results are not driven by the modeling choice made here.

### 2023-03-13 products/paper/supp_materials.qmd
Add footnote to main text regarding issue #33

```{r marg-fit-table}
#| label: tbl-marg-fit
#| tbl-cap: Marginal probabilities of grade retention by racial group across models using different specifications to model the the temporal trend in grade retention by current grade of the student.
marg_prob_alt %>%
  mutate(baseline=percent(round(baseline, 5)),
         year_dummy=percent(round(year_dummy, 5)),
         year_linear=percent(round(year_linear, 5)),
         year_dummy_interact=percent(round(year_dummy_interact, 5)),
         year_linear_interact=percent(round(year_linear_interact, 5)),
         year_grade_state=percent(round(year_grade_state, 5))) %>%
  kbl(booktabs=TRUE, linesep=NULL,
      align = c("l",rep("r", ncol(marg_prob_alt)-1)),
      col.names=c("Race", "No Covariates", "Year as dummy", 
                  "Year as linear", "Year (dummy) x Grade",
                  "Year (linear) x Grade", 
                  "Year (linear) x Grade and State")) %>%
  add_header_above(c(" " = 2, 
                     "Sensitivity tests on calendar year x grade coding" = 5)) %>%
  column_spec(2:7, width = "1.75cm") %>%
  footnote(general = "All models except no covariate case include dummies for current grade and state")
```

>>>>

```{r marg-fit-table}
#| label: tbl-marg-fit
#| tbl-cap: Marginal probabilities of being clearly behind expected grade by racial group across models using different specifications to model the the temporal trend in grade retention by current grade of the student.
marg_prob_alt %>%
  mutate(baseline=percent(round(baseline, 5)),
         year_dummy=percent(round(year_dummy, 5)),
         year_linear=percent(round(year_linear, 5)),
         year_dummy_interact=percent(round(year_dummy_interact, 5)),
         year_linear_interact=percent(round(year_linear_interact, 5)),
         year_grade_state=percent(round(year_grade_state, 5))) %>%
  kbl(booktabs=TRUE, linesep=NULL,
      align = c("l",rep("r", ncol(marg_prob_alt)-1)),
      col.names=c("Race", "No Covariates", "Year as dummy", 
                  "Year as linear", "Year (dummy) x Grade",
                  "Year (linear) x Grade", 
                  "Year (linear) x Grade and State")) %>%
  add_header_above(c(" " = 2, 
                     "Sensitivity tests on calendar year x grade coding" = 5)) %>%
  column_spec(2:7, width = "1.75cm") %>%
  footnote(general = "All models except no covariate case include dummies for current grade and state")
```
